\documentclass[a4paper,12pt]{report}

% Packages
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{hyperref}

% Page layout
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\setstretch{1.5}

% Title formatting
\titleformat{\chapter}[display]
{\normalfont\huge\bfseries}{\chaptername\ \thechapter}{20pt}{\Huge}

\begin{document}

% Title page
\begin{titlepage}
\begin{center}

    \rule{\linewidth}{0.5mm} \\[0.4cm]
    {\Huge \textbf{Internship Report}}\\[0.4cm]
    \rule{\linewidth}{0.5mm}\\[1cm]

    \textbf{ICT Department Internship}\\[1cm]

    \textbf{Submitted by:}\\[0.2cm]
    \textbf{[Your Full Name]}\\[0.2cm]
    \textbf{Student ID: [Your ID]}\\[1cm]

    \textbf{Supervisor: [Supervisor Name]}\\[0.2cm]
    \textbf{Position: [Supervisor Position]}\\[0.2cm]
    \textbf{Organization: ICT Department, College of Business and Economics}\\[1cm]

    \vfill

    \textbf{Submission Date: [Date]}\\[0.5cm]

\end{center}

\end{titlepage}

% Table of contents
\tableofcontents
\newpage

% Chapter 1: Introduction
\chapter{Introduction}
\section{Overview of the Internship}
The internship program is a key component of the academic curriculum designed to provide students with hands-on experience in their field of study. This report documents my internship experience at the ICT Department of the University of Rwanda, College of Business and Economics (CBE), Gikondo Campus. The internship aimed to bridge the gap between theoretical knowledge and practical application in the field of Information and Communication Technology (ICT).

\section{Objectives of the Internship}
\begin{itemize}
\item To gain practical experience in ICT operations and services.
\item To develop technical skills in troubleshooting and maintaining ICT systems.
\item To understand the role of ICT in supporting academic and administrative functions.
\end{itemize}

% Chapter 2: Organizational Profile
\chapter{Organizational Profile}
\section{About the University of Rwanda}
The University of Rwanda is the largest higher education institution in Rwanda, offering a wide range of academic programs. The College of Business and Economics (CBE) at Gikondo Campus is a hub for students pursuing degrees in business-related fields.

\section{ICT Department Overview}
The ICT Department is responsible for managing the campus’s technological infrastructure, including:
\begin{itemize}
\item Maintaining computer labs and network systems.
\item Providing technical support to students and staff.
\item Ensuring data security and system reliability.
\end{itemize}

% Chapter 3: Internship Activities
\chapter{Internship Activities}
\section{Assigned Tasks}
During my internship, I was assigned the following tasks:
\begin{itemize}
\item Assisting in troubleshooting and resolving hardware and software issues.
\item Configuring and maintaining network devices and systems.
\item Providing technical support for events and online systems.
\item Updating and documenting ICT inventory.
\end{itemize}

\section{Key Projects}
\subsection{Network Maintenance}
I participated in diagnosing and resolving network connectivity issues across the campus. This involved configuring routers and switches, as well as monitoring network performance.

\subsection{System Upgrades}
I assisted in upgrading outdated software and ensuring compatibility with the university’s systems. This included testing and deploying new applications.

\subsection{Technical Support}
I provided support to staff and students by resolving login issues, setting up devices, and addressing software errors.

% Chapter 4: Skills and Knowledge Acquired
\chapter{Skills and Knowledge Acquired}
\section{Technical Skills}
\begin{itemize}
\item Proficiency in network configuration and troubleshooting.
\item Hands-on experience with ICT hardware and software maintenance.
\item Familiarity with data management and security protocols.
\end{itemize}

\section{Soft Skills}
\begin{itemize}
\item Improved communication and teamwork abilities.
\item Enhanced problem-solving and critical thinking skills.
\item Time management and organizational skills.
\end{itemize}

% Chapter 5: Challenges and Recommendations
\chapter{Challenges and Recommendations}
\section{Challenges Faced}
\begin{itemize}
\item Limited access to advanced hardware and software tools.
\item Occasional delays in resolving technical issues due to resource constraints.
\item Balancing multiple tasks within tight deadlines.
\end{itemize}

\section{Recommendations}
\begin{itemize}
\item Increase access to modern ICT equipment for interns.
\item Provide regular training sessions to enhance technical expertise.
\item Improve resource allocation to ensure timely resolution of issues.
\end{itemize}

% Chapter 6: Conclusion
\chapter{Conclusion}
The internship at the ICT Department of the University of Rwanda, CBE, Gikondo Campus, provided invaluable practical experience and insights into the role of ICT in academic environments. The skills and knowledge gained during this period have significantly enhanced my understanding of ICT operations and prepared me for future professional challenges.

% References (if any)
\chapter*{References}
\addcontentsline{toc}{chapter}{References}
[Include references if applicable]

\end{document}